Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-03-25 chSPIE_2012_CA1/article.tex
transform SPIE 2012 CA1 article into a chapter, update references, hope it compiles

\documentclass[]{spie}  
\usepackage{subfig}
\usepackage{color}
\usepackage[]{graphicx}

\title{Near infrared metrology of high performance silicon immersion gratings}

%>>>> The author is responsible for formatting the 
%  author list and their institutions.  Use  \skiplinehalf 
%  to separate author list from addresses and between each address.
%  The correspondence between each author and his/her address
%  can be indicated with a superscript in italics, 
%  which is easily obtained with \supit{}.

\author{Michael Gully-Santiago\supit{a}, Weisong Wang\supit{a}, Casey Deen\supit{a,b}, Daniel Jaffe\supit{a}
\skiplinehalf
\supit{a}The University of Texas at Austin Department of Astronomy, 1 University Station C1400, Austin, TX 78712, USA; \\
\supit{b} current afilliation: Max-Planck Institut f\"{u}r Astronomie K\"{o}nigstuhl 17, D-69117 Heidelberg, Germany}

%\authorinfo{Further author information: (Send correspondence to A.A.A.)\\A.A.A.: E-mail: aaa@tbk2.edu, Telephone: 1 505 123 1234\\  B.B.A.: E-mail: bba@cmp.com, Telephone: +33 (0)1 98 76 54 32}
% \pagestyle{plain}    
%\setcounter{page}{301}

  \begin{document} 
  \maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
Silicon immersion gratings offer size and cost savings for high-resolution near-infrared spectrographs.  The IGRINS instrument at McDonald Observatory will employ a high-performance silicon immersion echelle grating to achieve spectral resolution $R=\frac{\lambda}{\Delta \lambda}40,000$ simultaneously over H and K near-infrared band atmospheric windows (1.5$-$2.5 $\mu$m).  We chronicle the metrology of an R3 silicon immersion echelle grating for IGRINS.  The grating is 30 $\times$ 80 mm, etched into a monolithic silicon prism.  Optical interferometry of the grating surface in reflection indicates high phase coherence ($< \lambda/6$ peak to valley surface error over a 25 mm beam at $\lambda=632$ nm).  Optical interferometry shows small periodic position errors of the grating grooves.  These periodic errors manifest as spectroscopic ghosts.  High dynamic range monochromatic spectral purity measurements reveal ghost levels relative to the main diffraction peak at $1.6 \times 10^{-3}$ at $\lambda = 632$ nm in reflection, consistent with the interferometric results  Improved grating surfaces demonstrate reflection-measured ghosts at negligible levels of $10^{-4}$ of the main diffraction peak.  Relative on-blaze efficiency is $\sim$75\%.  We investigate the immersion grating blaze efficiency performance over the entire operational bandwidth $1500 < \lambda(nm) < 2500$ at room temperature.  The projected performance at operational cryogenic temperatures meets the design specifications.
\end{abstract}

%>>>> Include a list of keywords after the abstract

\keywords{Immersion, Diffraction, Gratings, Infrared, Spectroscopy, Lithography, Silicon}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
\label{sec:intro}

@@

\begin{figure}
  \centering
  \subfloat[CA1a photo]{\label{fig:CA1aphoto}\includegraphics[height=5cm]{ca1_bartest2}}
	~
%  \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[page=1, trim=24cm 15.15cm 2cm 5cm, clip=true, totalheight=0.2\textheight ]{APRA_BOULE_29MM_R3_CA1_X14_2011-03-08}}
   \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[height=4cm]{ca1a_drawing}}
  \caption{Photo and design drawing of the immersion grating CA1a in the lab in August 2011.  The entrance face is on the right, with a light green color in the photo (color available in the digital manuscript), which is due to the AR coating.  The grating surface is on the top with microscopic grating lines perpendicular to the long edge of the grating.  In operation a 25 mm circular beam will be incident on the entrance face and will project into an ellipse on the grating surface as seen in the drawing.  The dispersed light will reemerge from the entrance face.  The units in the drawing are mm.  The parent substrate and grating geometry are pictured in Figures 1, 3, and 4 in Wang et al. 2010\cite{wang2010}.  Those figures reveal how the CA1a trapezoid shape and curved rear edge derive from the parent substrate shape.}
  \label{fig:gram}
\end{figure}

@@

%-------------
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=7cm]{CA1_SEM_cross3}
   \end{tabular}
   \end{center}
   \caption[CA1a SEM]{ \label{fig:CA1aSEM}  Scanning electron micrograph (SEM) of a $\sim$100 $\mu$m cross section of a scrap portion of the immersion grating CA1.  The left panel is the unaltered SEM.  The right panel is a schematic illustrating the grating specifications and the geometry of incident and diffracted beams (thick black line with arrows).  The beam is incident from the left, and diffracts at the facets at the silicon/aluminum interface.  The incident angle $\alpha$ and diffracted beam $\beta$ are measured from the grating normal (shown in blue).  The blaze angle $\delta$ is set by the orientation of the crystal planes with respect to the grating surface.  This angle was designed to be $\delta=71.56^\circ$, which is the angle whose tangent is 3.  The optically active facets are highlighted as short red vertical lines (\emph{color online}).  The regions of the grating above the dashed line do not see the beam.  In the IGRINS design and in our lab testing there is a small out of plane angle $\gamma$ not shown here.  The apparent hillock artifacts on the grating facets are a result of the cross-section preparation process, the measured\cite{wang2010} surface flatness is 1.7 nm.}
   \end{figure} 
%-------------

\section{Efficiency} 
For optimal performance immersion gratings should be as efficient as possible.  The IGRINS specification for immersion grating efficiency is 65-70\% peak on blaze\cite{wang2010}. We directly measured the AR-coated entrance face reflective loss at $<1\%$ over the measured range $1500-2300$ nm.  From measurements of the microscopic surface roughness\cite{wang2010} we expect scattered light from microscopic surface roughness to be $<0.5\%$.  We directly measured the immersion grating efficiency as a function of wavelength with a custom scanning monochromator setup in our lab, described in the Appendix Section \ref{sec:GTA}.  The reference mirror was aluminum on glass, so the absolute grating efficiency is about 3.5\% lower than reported here, assuming aluminum reflectance of 95\% in the near-IR.  Recall that the grating grooves are aluminized, so the reported relative efficiency is a good indicator of how well the bulk of the immersion grating is performing.  The measurement shown in figure \ref{fig:CA1a-efficiency} has 1 nm bandwidth, with 1nm sampling over the range $1500-2300$ nm.  The measured peak on-blaze efficiency is between 70\% and 80\% across all 43 orders, except for order 120 which has a peak efficiency of 68\%.  CA1a was measured with an out of plane angle \cite{schroeder1987}, $\gamma \sim 2.6^\circ$ in immersion.  We only coarsely controlled the incidence angle $\alpha$ in our efficiency measurement, with $\alpha \sim \delta$ to within about 2$^\circ$.  Accordingly, we measured some angularly dependent diffraction loss that one would expect if orders diffracted into the grating sidewalls.  It is best to have $\alpha > \delta$ so that the blaze envelope is centered at $\beta < \delta$.

\begin{figure}
\begin{center}
 \begin{tabular}{c}
    \includegraphics[width=1.0\textwidth]{CA1a_1500_2300_eff.pdf}
   \end{tabular}
  \end{center}
  \caption[CA1a Efficiency]{\label{fig:CA1a-efficiency} Efficiency of CA1a as a function of wavelength.  The measurements for 1500$-$2300 nm cover orders 120 to 78.  The peak on-blaze efficiency is typically about 75\% of an aluminum reference mirror, as shown by the horizontal dotted line at 75\%.  The vertical dashed lines at 1450 and 1900 nm demarcate the designed wavelength range of IGRINS $H-$band channel.  Similarly, the vertical dash triple-dotted lines demarcate the $K-$band channel.  The faint gray line in the background is the atmospheric transmission over Kitt Peak\cite{hinkle1995}.  Measurements at $\lambda > 2300 $ nm we not performed at the time of writing.  The slightly suppressed efficiency at 1500 nm may result from visible light leakage in the reference mirror measurement from our 1450 nm low pass filter operated in uncollimated light, or perhaps from real polarization sensitive effects.  See the notes on the next figure's caption regarding the difference in measurements shortward and longward of 1870 nm.}
\end{figure}

@@

\begin{figure}
\begin{center}
 \begin{tabular}{c}
    \includegraphics[width=1.0\textwidth]{CA1a_diffrac}
   \end{tabular}
  \end{center}
  \caption[CA1a Diffraction]{\label{fig:CA1a-diffrac} Measured and predicted diffraction angles for CA1a.  The right panel is the index of refraction as a function of wavelength\cite{frey2006} for T = 296, 273, and 77 K.  The left panel is the angular position of diffracted beams as a function of wavelength.  The almost vertical lines are approximately 1 free spectral range of the observed 43 diffraction orders for $1500 < \lambda (\textrm{nm}) < 2300$ in air at T = 296K.  The order numbers for every fifth order, starting at 78th order are marked at the top.  The black diamonds are the observed peaks of the blaze efficiency (cf. figure \ref{fig:CA1a-efficiency}).  The measurements longward and shortward of $\lambda=1870$ nm have slightly different incidence $\alpha$ angles, which jogged the the blaze center positions.  The red $\ast$, green square, and blue $\times$ demarcate the expected positions of beams from scalar optics diffraction and refraction theory assuming a Si refractive index at the temperatures of T=296, 273, and 77 K, respectively.  The model corrects for $\alpha \neq \delta$ measurements for $\lambda < 1870 $ nm, causing a jog in the $\theta(\lambda)$ trend highlighted by the vertical black dashed lines.  The temperature change shifts the position of diffracted beams by an entire order.}
\end{figure}

@@

\begin{figure}
  \centering
\includegraphics[width=0.9\textwidth]{CA1a_fig_scl2}
  \caption{Optical interferometry of CA1a in reflection off the back surface before cutting and aluminization.  The color scales are in waves of surface error for 632 nm in reflection.  \emph{Left:} Interferogram measured in Littrow reflection at R3 over a 23.75 mm beam on the parent substrate CA1, in the vicinity where CA1a was later cut.  The colorbars show the vertical scale in waves of surface distortion at $\lambda = $ 632.8 nm.  These optical measurements illuminate the back of the grating facets, they were taken before aluminization and should be a good proxy for immersion performance at 2.15 $\mu$m. \emph{Center:} A fit to the large scale surface distortion using the first 200 Zernike polynomials in the Noll Sequence \cite{noll1976}.  \emph{Right:} The residual high spatial frequency surface error constructed from subtracting the fit from the measured surface error.}
  \label{fig:gram}
\end{figure}

@@

\begin{figure}
\begin{center}
 \subfloat[2D Zygo PSF]{\label{fig:zygoPSF2D} \includegraphics[width=0.45\textwidth]{CA1a_ghost_zygo_2d}}
 \subfloat[1D Log PSF]{\label{fig:logPSF1D} \includegraphics[width=0.45\textwidth]{CA1a_ghost_1d}}   
  \end{center}
  \caption[Immersion grating interferogram PSF]{\label{fig:PSFzygo}  Left: The 2-dimensional synthetic PSF from interferometric measurements of the air-aluminum reflective interface of CA1a at 632.8 nm at R3.  The dispersion direction is $x$, the cross-dispersion or spatial dimension is $y$.  The units on the axes are in terms of diffraction widths of $\lambda=$ 632.8 nm and $D=$ 25 mm, which were the conditions of the interferometry.  The scale on the 2D image is linear, compare to the intensity levels shown on the right panel.  Right:  The 1D logarithmically scaled horizontal line profile of the PSF of CA1a under three conditions.  The black is the synthetic interferometric PSF.  The red is the lab-measured PSF in reflection at 632 nm with a 20 mm beam.  This measurement is not diffraction limited.  The green line is the measurement at 543 nm in reflection with a 20 mm beam.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix    %>>>> this command starts appendixes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Measurement setup description} \label{sec:GTA}
The basic strategy of the custom efficiency measurement setup is to compare the chopped signal from the immersion grating to an aluminum mirror.  The monochromator outputs 1 nm bandwidth and we sample at 1 nm steps.  The basic layout is a light source, 1.45 $\mu$m long pass filter, Spectral Products DK480 scanning monochromator, a chopper, collimating and relay optics, a motorized swing arm, a single pixel PbS array, and a lock-in amplifier.  The DK480, motorized swing arm, and lock-in amplifier are all computer controlled.  Custom software predicts the diffraction angles of the immersion grating and fine scans the swing arm around the predicted angular order positions.  Figure \ref{fig:GTAview} shows a labelled photo of the measurement apparatus, with detailed description of the optical path in the figure caption.

\begin{figure}
\begin{center}
    \includegraphics[width=1.0\textwidth]{GTA_cam_model_ref_tilt.jpg}
  \end{center}
  \caption[View of the monochromator, periscope, and swing arm-camera system with the beam path highlighted]{\label{fig:GTAview} View of the monochromator, periscope, and swing arm-camera system with the beam path highlighted.  The beam exits the monochromator exit slit (8), where the optical chopper (9) is located.  The beam is collimated by a 1 inch post-slit lens (10).  The periscope system includes 3 mirrors (12, 13a, 13b), only two of which are active at any time.  In the reflective arm of interest to this report, we use mirrors (12) and (13b), with mirror 13a moved clear out of the beam path with a 90$^\circ$ flip mount.  The beam travels about 1 meter (off the image) to an adjustable iris in double pass (14, 16) sandwiching a mirror (15) tilted about 10$^\circ$ from the $z-y$ plane.  The beam travels along the vector terminating on the center of the immersion grating (17).  The immersion grating has its grooves vertical (parallel to the $z-$axis) so that the dispersion occurs in a the $x-y$ plane.  There are typically 3 or 4 orders diffracted $\pm20^\circ$ from the optical axis, for CA1 in our wavelength range of interest ($1.5-2.5 \; \mu$m).  The camera lens (18) and single pixel detector (19) are mounted on a swinging arm which rotates in the $x-y$ plane, with its center of rotation equal to the position of the immersion grating.  The angular range of motion of the swing arm is about +27 to -37$^\circ$ which is set by limit switches and the rigid mechanical structure, which supports the immersion grating and its concomitant fine adjust positioning hardware.  The cartoon arrows demonstrate our angular sign convention which is positive counter clockwise, with zero along the optic axis.  The grating normal is at about -70$^\circ$ with that convention.  The beam path in the monochromator is omitted for clarity.  The lock-in amplifier electronics are marked with number (20).}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments     %>>>> equivalent to \section*{ACKNOWLEDGMENTS}

Portions of this work were supported by NASA APRA grant NNX10AC68G and NSF ATI grant AST-0705064.  MGS was supported by the NASA Graduate Student Researchers Program (GSRP) grant number NNX10AK82H.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% References %%%%%

\bibliography{report}   %>>>> bibliography data in report.bib
\bibliographystyle{spiebib}   %>>>> makes bibtex use spiebib.bst

\end{document}

>>>>

\chapter{Near infrared metrology of high performance silicon immersion gratings}

\section{Introduction}
\label{sec:intro}

@@

\begin{figure}
  \centering
  \subfloat[CA1a photo]{\label{fig:CA1aphoto}\includegraphics[height=5cm]{chSPIE_2012_CA1/figs/ca1_bartest2}}
	~
%  \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[page=1, trim=24cm 15.15cm 2cm 5cm, clip=true, totalheight=0.2\textheight ]{APRA_BOULE_29MM_R3_CA1_X14_2011-03-08}}
   \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[height=4cm]{chSPIE_2012_CA1/figs/ca1a_drawing}}
  \caption{Photo and design drawing of the immersion grating CA1a in the lab in August 2011.  The entrance face is on the right, with a light green color in the photo (color available in the digital manuscript), which is due to the AR coating.  The grating surface is on the top with microscopic grating lines perpendicular to the long edge of the grating.  In operation a 25 mm circular beam will be incident on the entrance face and will project into an ellipse on the grating surface as seen in the drawing.  The dispersed light will reemerge from the entrance face.  The units in the drawing are mm.  The parent substrate and grating geometry are pictured in Figures 1, 3, and 4 in Wang et al. 2010\cite{wang2010}.  Those figures reveal how the CA1a trapezoid shape and curved rear edge derive from the parent substrate shape.}
  \label{fig:gram}
\end{figure}

@@

%-------------
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=7cm]{chSPIE_2012_CA1/figs/CA1_SEM_cross3}
   \end{tabular}
   \end{center}
   \caption[CA1a SEM]{ \label{fig:CA1aSEM}  Scanning electron micrograph (SEM) of a $\sim$100 $\mu$m cross section of a scrap portion of the immersion grating CA1.  The left panel is the unaltered SEM.  The right panel is a schematic illustrating the grating specifications and the geometry of incident and diffracted beams (thick black line with arrows).  The beam is incident from the left, and diffracts at the facets at the silicon/aluminum interface.  The incident angle $\alpha$ and diffracted beam $\beta$ are measured from the grating normal (shown in blue).  The blaze angle $\delta$ is set by the orientation of the crystal planes with respect to the grating surface.  This angle was designed to be $\delta=71.56^\circ$, which is the angle whose tangent is 3.  The optically active facets are highlighted as short red vertical lines (\emph{color online}).  The regions of the grating above the dashed line do not see the beam.  In the IGRINS design and in our lab testing there is a small out of plane angle $\gamma$ not shown here.  The apparent hillock artifacts on the grating facets are a result of the cross-section preparation process, the measured\cite{wang2010} surface flatness is 1.7 nm.}
   \end{figure} 
%-------------

\section{Efficiency} 
For optimal performance immersion gratings should be as efficient as possible.  The IGRINS specification for immersion grating efficiency is 65-70\% peak on blaze\cite{wang2010}. We directly measured the AR-coated entrance face reflective loss at $<1\%$ over the measured range $1500-2300$ nm.  From measurements of the microscopic surface roughness\cite{wang2010} we expect scattered light from microscopic surface roughness to be $<0.5\%$.  We directly measured the immersion grating efficiency as a function of wavelength with a custom scanning monochromator setup in our lab, described in the Section \ref{sec:GTA}.  The reference mirror was aluminum on glass, so the absolute grating efficiency is about 3.5\% lower than reported here, assuming aluminum reflectance of 95\% in the near-IR.  Recall that the grating grooves are aluminized, so the reported relative efficiency is a good indicator of how well the bulk of the immersion grating is performing.  The measurement shown in figure \ref{fig:CA1a-efficiency} has 1 nm bandwidth, with 1nm sampling over the range $1500-2300$ nm.  The measured peak on-blaze efficiency is between 70\% and 80\% across all 43 orders, except for order 120 which has a peak efficiency of 68\%.  CA1a was measured with an out of plane angle \cite{schroeder1987}, $\gamma \sim 2.6^\circ$ in immersion.  We only coarsely controlled the incidence angle $\alpha$ in our efficiency measurement, with $\alpha \sim \delta$ to within about 2$^\circ$.  Accordingly, we measured some angularly dependent diffraction loss that one would expect if orders diffracted into the grating sidewalls.  It is best to have $\alpha > \delta$ so that the blaze envelope is centered at $\beta < \delta$.

\begin{figure}
\begin{center}
 \begin{tabular}{c}
    \includegraphics[width=1.0\textwidth]{chSPIE_2012_CA1/figs/CA1a_1500_2300_eff.pdf}
   \end{tabular}
  \end{center}
  \caption[CA1a Efficiency]{\label{fig:CA1a-efficiency} Efficiency of CA1a as a function of wavelength.  The measurements for 1500$-$2300 nm cover orders 120 to 78.  The peak on-blaze efficiency is typically about 75\% of an aluminum reference mirror, as shown by the horizontal dotted line at 75\%.  The vertical dashed lines at 1450 and 1900 nm demarcate the designed wavelength range of IGRINS $H-$band channel.  Similarly, the vertical dash triple-dotted lines demarcate the $K-$band channel.  The faint gray line in the background is the atmospheric transmission over Kitt Peak\cite{hinkle1995}.  Measurements at $\lambda > 2300 $ nm we not performed at the time of writing.  The slightly suppressed efficiency at 1500 nm may result from visible light leakage in the reference mirror measurement from our 1450 nm low pass filter operated in uncollimated light, or perhaps from real polarization sensitive effects.  See the notes on the next figure's caption regarding the difference in measurements shortward and longward of 1870 nm.}
\end{figure}

@@

\begin{figure}
\begin{center}
 \begin{tabular}{c}
    \includegraphics[width=1.0\textwidth]{chSPIE_2012_CA1/figs/CA1a_diffrac}
   \end{tabular}
  \end{center}
  \caption[CA1a Diffraction]{\label{fig:CA1a-diffrac} Measured and predicted diffraction angles for CA1a.  The right panel is the index of refraction as a function of wavelength\cite{frey2006} for T = 296, 273, and 77 K.  The left panel is the angular position of diffracted beams as a function of wavelength.  The almost vertical lines are approximately 1 free spectral range of the observed 43 diffraction orders for $1500 < \lambda (\textrm{nm}) < 2300$ in air at T = 296K.  The order numbers for every fifth order, starting at 78th order are marked at the top.  The black diamonds are the observed peaks of the blaze efficiency (cf. figure \ref{fig:CA1a-efficiency}).  The measurements longward and shortward of $\lambda=1870$ nm have slightly different incidence $\alpha$ angles, which jogged the the blaze center positions.  The red $\ast$, green square, and blue $\times$ demarcate the expected positions of beams from scalar optics diffraction and refraction theory assuming a Si refractive index at the temperatures of T=296, 273, and 77 K, respectively.  The model corrects for $\alpha \neq \delta$ measurements for $\lambda < 1870 $ nm, causing a jog in the $\theta(\lambda)$ trend highlighted by the vertical black dashed lines.  The temperature change shifts the position of diffracted beams by an entire order.}
\end{figure}

@@

\begin{figure}
  \centering
\includegraphics[width=0.9\textwidth]{chSPIE_2012_CA1/figs/CA1a_fig_scl2}
  \caption{Optical interferometry of CA1a in reflection off the back surface before cutting and aluminization.  The color scales are in waves of surface error for 632 nm in reflection.  \emph{Left:} Interferogram measured in Littrow reflection at R3 over a 23.75 mm beam on the parent substrate CA1, in the vicinity where CA1a was later cut.  The colorbars show the vertical scale in waves of surface distortion at $\lambda = $ 632.8 nm.  These optical measurements illuminate the back of the grating facets, they were taken before aluminization and should be a good proxy for immersion performance at 2.15 $\mu$m. \emph{Center:} A fit to the large scale surface distortion using the first 200 Zernike polynomials in the Noll Sequence \cite{noll1976}.  \emph{Right:} The residual high spatial frequency surface error constructed from subtracting the fit from the measured surface error.}
  \label{fig:gram}
\end{figure}

@@

\begin{figure}
\begin{center}
 \subfloat[2D Zygo PSF]{\label{fig:zygoPSF2D} \includegraphics[width=0.45\textwidth]{chSPIE_2012_CA1/figs/CA1a_ghost_zygo_2d}}
 \subfloat[1D Log PSF]{\label{fig:logPSF1D} \includegraphics[width=0.45\textwidth]{chSPIE_2012_CA1/figs/CA1a_ghost_1d}}   
  \end{center}
  \caption[Immersion grating interferogram PSF]{\label{fig:PSFzygo}  Left: The 2-dimensional synthetic PSF from interferometric measurements of the air-aluminum reflective interface of CA1a at 632.8 nm at R3.  The dispersion direction is $x$, the cross-dispersion or spatial dimension is $y$.  The units on the axes are in terms of diffraction widths of $\lambda=$ 632.8 nm and $D=$ 25 mm, which were the conditions of the interferometry.  The scale on the 2D image is linear, compare to the intensity levels shown on the right panel.  Right:  The 1D logarithmically scaled horizontal line profile of the PSF of CA1a under three conditions.  The black is the synthetic interferometric PSF.  The red is the lab-measured PSF in reflection at 632 nm with a 20 mm beam.  This measurement is not diffraction limited.  The green line is the measurement at 543 nm in reflection with a 20 mm beam.}
\end{figure}

\section{Measurement setup description} \label{sec:GTA}
The basic strategy of the custom efficiency measurement setup is to compare the chopped signal from the immersion grating to an aluminum mirror.  The monochromator outputs 1 nm bandwidth and we sample at 1 nm steps.  The basic layout is a light source, 1.45 $\mu$m long pass filter, Spectral Products DK480 scanning monochromator, a chopper, collimating and relay optics, a motorized swing arm, a single pixel PbS array, and a lock-in amplifier.  The DK480, motorized swing arm, and lock-in amplifier are all computer controlled.  Custom software predicts the diffraction angles of the immersion grating and fine scans the swing arm around the predicted angular order positions.  Figure \ref{fig:GTAview} shows a labelled photo of the measurement apparatus, with detailed description of the optical path in the figure caption.

\begin{figure}
\begin{center}
    \includegraphics[width=1.0\textwidth]{chSPIE_2012_CA1/figs/GTA_cam_model_ref_tilt.jpg}
  \end{center}
  \caption[View of the monochromator, periscope, and swing arm-camera system with the beam path highlighted]{\label{fig:GTAview} View of the monochromator, periscope, and swing arm-camera system with the beam path highlighted.  The beam exits the monochromator exit slit (8), where the optical chopper (9) is located.  The beam is collimated by a 1 inch post-slit lens (10).  The periscope system includes 3 mirrors (12, 13a, 13b), only two of which are active at any time.  In the reflective arm of interest to this report, we use mirrors (12) and (13b), with mirror 13a moved clear out of the beam path with a 90$^\circ$ flip mount.  The beam travels about 1 meter (off the image) to an adjustable iris in double pass (14, 16) sandwiching a mirror (15) tilted about 10$^\circ$ from the $z-y$ plane.  The beam travels along the vector terminating on the center of the immersion grating (17).  The immersion grating has its grooves vertical (parallel to the $z-$axis) so that the dispersion occurs in a the $x-y$ plane.  There are typically 3 or 4 orders diffracted $\pm20^\circ$ from the optical axis, for CA1 in our wavelength range of interest ($1.5-2.5 \; \mu$m).  The camera lens (18) and single pixel detector (19) are mounted on a swinging arm which rotates in the $x-y$ plane, with its center of rotation equal to the position of the immersion grating.  The angular range of motion of the swing arm is about +27 to -37$^\circ$ which is set by limit switches and the rigid mechanical structure, which supports the immersion grating and its concomitant fine adjust positioning hardware.  The cartoon arrows demonstrate our angular sign convention which is positive counter clockwise, with zero along the optic axis.  The grating normal is at about -70$^\circ$ with that convention.  The beam path in the monochromator is omitted for clarity.  The lock-in amplifier electronics are marked with number (20).}
\end{figure}

### 2015-03-25 gullydiss.tex
woohoo, it compiles!
rename SPIE_2014_ebeam.tex, ignore the sublime files
transform SPIE 2012 CA1 article into a chapter, update references, hope it compiles

@@

\include{chSPIE_2014_ebeam/SPIE_2014_ebeam}

>>>>

\emph{Immersion Grating abstract}
Silicon immersion gratings offer size and cost savings for high-resolution near-infrared spectrographs.  The IGRINS instrument at McDonald Observatory will employ a high-performance silicon immersion echelle grating to achieve spectral resolution $R=\frac{\lambda}{\Delta \lambda}40,000$ simultaneously over H and K near-infrared band atmospheric windows (1.5$-$2.5 $\mu$m).  We chronicle the metrology of an R3 silicon immersion echelle grating for IGRINS.  The grating is 30 $\times$ 80 mm, etched into a monolithic silicon prism.  Optical interferometry of the grating surface in reflection indicates high phase coherence ($< \lambda/6$ peak to valley surface error over a 25 mm beam at $\lambda=632$ nm).  Optical interferometry shows small periodic position errors of the grating grooves.  These periodic errors manifest as spectroscopic ghosts.  High dynamic range monochromatic spectral purity measurements reveal ghost levels relative to the main diffraction peak at $1.6 \times 10^{-3}$ at $\lambda = 632$ nm in reflection, consistent with the interferometric results  Improved grating surfaces demonstrate reflection-measured ghosts at negligible levels of $10^{-4}$ of the main diffraction peak.  Relative on-blaze efficiency is $\sim$75\%.  We investigate the immersion grating blaze efficiency performance over the entire operational bandwidth $1500 < \lambda(nm) < 2500$ at room temperature.  The projected performance at operational cryogenic temperatures meets the design specifications.

@@

\include{chSPIE_2014_ebeam/chapter-2014-ebeam}
\include{chSPIE_2012_CA1a/article}
